Initial Analysis

### 2019-10-14 Initial_Analysis.Rmd

## Sub Routine Estimating Neighbourds

@@

### Estimate Transboundary Species

@@

## Function `EstSppStatus`

  Data <- GetSppDist(Spp, Model = "SAU_C", Coord = Coord) %>% 
    gather("Year","Value",CATCH.1:CATCH.65) %>% 
    arrange(INDEX) %>% 
    mutate(Year = rep(seq(1951,2014,1),263250)) %>% 
    left_join(Index_Code,
              by = "INDEX") %>% 
    filter(!is.na(EEZID),
           Value > 0) %>% 
    group_by(Species,Year,Territory) %>% # Total catch per country
    summarise(Total_Catch = sum(Value,na.rm=T)) %>% 
    group_by(Species,Territory,Year) %>% 
    mutate(RMean = rollmean(x = Total_Catch, 3,
                            align = "right",
                            fill = Total_Catch)
           ) %>% # Running mean
    group_by(Species,Territory) %>% 
    select(-Total_Catch)

  # Tresholds to evaluate stocks if these are not met, then soecies status = "No Status"
  Tresholds_Data <- Data %>% 
    arrange(Territory) %>% 
    group_by(Species,Territory, grp = cumsum(c(1, diff(Year) != 65))) %>% 
    group_by(Species,Territory) %>% 
    summarise(Years_appart = ifelse(max(Year)-min(Year) >= 0,"Yes","No"), # Step 1. first and last reported landings are at least 10 years apart
              Consecutive = ifelse(max(grp) >= 5,"Yes","No"), # Step 2. There are at least 5 consecutive catch years
              Catch_over = ifelse(max(RMean >= 1000),"Yes","No") # Step 3. 3) The catch in a particular area (LME) is at least 1,000 tonnes.
    ) %>% 
    gather("Step","Treshold",Years_appart:Catch_over) %>% 
    group_by(Species,Territory) %>% 
    summarise(Met_Criteria = paste(unique(Treshold),collapse =";")
              )

    No_Status_Data <- Tresholds_Data %>% 
      filter(Met_Criteria != "Yes") %>% 
      select(Species,Territory) %>% 
      mutate(Status = "No Status")

    # Get Variables to perform status metric
    Status_Data <- Data %>% 
      anti_join(No_Status_Data, # Removes no status data
                by = c("Species","Territory")
      ) %>% 
      # Get Max catch and max catch year
      group_by(Species,Territory) %>% 
      top_n(1,RMean) %>% 
      rename(Max_Peak = RMean,
             Y_Max_Peak = Year) %>% 
      # Get Min catch after peak catch
      left_join(Data,
                by = c("Species","Territory")
                ) %>% 
      filter(Year > Y_Max_Peak) %>% 
      group_by(Species,Territory) %>% 
      top_n(-1,RMean) %>% 
      rename(Post_Max_Min = RMean,
             Y_Post_Max_Min = Year) %>% 
      left_join(Data,
                by = c("Species","Territory")
                ) %>% 
      # Final Evaluation 
      mutate(Status = ifelse(Year > Y_Post_Max_Min & Post_Max_Min < (Max_Peak*0.10) & (RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50)),"Rebuilding",
                             ifelse((Year < Y_Max_Peak & RMean <= (Max_Peak*0.50) | Y_Max_Peak == max(Year)),"Developing",
                                    ifelse(RMean > Max_Peak*0.50,"Max Exploited",
                                           ifelse(Year > Y_Max_Peak & (RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50)),"Over Exploited",
                                                  ifelse(Year > Y_Max_Peak & RMean < Max_Peak*0.10,"Collapsed",
                                                         "No Status")
                                           )
                                    )
                             )
      )
      ) %>% 
      filter(Year > 2004) %>% # last 10 years of data
      group_by(Species,Territory,Status) %>% 
      summarise(n_Status= n()) %>% 
      group_by(Species,Territory) %>% 
      top_n(1,n_Status) %>%
      select(-n_Status)

Species_Status <- bind_rows(
    mclapply(
      Species_List,
      FUN = EstSppStatus,
      Coord = CoorG  # Gabriels coordinate system for read species dist
    )
  )

@@

@@

# Data per Territory
Transboundary_Spp <- Tresholded_T_Data %>% 
  group_by(Territory) %>% 
  summarise(
    n_trans_spp = length(unique(TaxonKey)),
    n_Neighbours = length(unique(Neighbour)),
    Trans_Rate = n_trans_spp/n_Neighbours
    )

@@

@@

World_sf_si <- World_sf %>%
  st_transform(crs = 4326) %>% # 4326
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
  left_join(Transboundary_Spp, by ="Territory")

#  Top 10 Larger EEZs...
# World_sf_si %>% 
#   arrange(desc(Area_km2)) %>% 
#   head(10)

Revenue_Country <- sau_eez_fes %>% 
  group_by(fishing_entity_id, Territory = fishing_entity) %>% 
  summarise(n=n()) %>% 
  select(-n) %>% 
  left_join(Tresholded_T_Data_x) %>% 
  left_join(Sau_Revenue_Data) %>% 
  group_by(Territory) %>% 
  summarise(Total_USD = sum(Mean_Value,na.rm=T)) %>% 
  mutate(Territory = ifelse(Territory == "USA","United States of America",Territory))

hist(Revenue_Country$Total_USD)

World_sf_si_land <- World_land_sf %>%
  st_transform(crs = 4326) %>% # 4326
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%  # Include transboundary species
  left_join(Revenue_Country, by ="Territory") # Include total specices catch

# head(World_sf_si)s

# Create a pellet for plotting
# pal <- wes_palette("Zissou1", 1000, type = "continuous")

World_sf_si$Bins <- cut(World_sf_si$n_trans_spp,breaks = 4)
World_sf_si_land$Bins <- cut(World_sf_si_land$Total_USD,breaks = 4)

World_sf_si_land <- World_sf_si_land %>% 
  arrange(Total_USD)

World_sf_si <- World_sf_si %>% 
  arrange(n_trans_spp)

# head(World_sf_si)
# head(World_sf_si_land)

# unique(World_sf_si$Bins)
# unique(World_sf_si_land$BinsLan)

# levels(World_sf_si$Bins)
# levels(World_sf_si_land$BinsLan)

@@

Plot <- ggplot() +
  geom_sf(data = World_sf_si_land,aes(fill = Bins), colour = "grey80",size = 0.1) +
  geom_sf(data = World_sf_si,aes(fill = Bins),colour = "grey20", size = 0.1) + # n_trans_spp or Bins
  geom_sf(data = Grey_land,aes(fill = Bins),fill = "grey80", colour = "grey50",size = 0.1) + # n_trans_spp or Bins
  # scale_fill_gradientn(colours = pal,
  #                      na.value = "white") +
  # scale_fill_manual(values = c(rev(wes_palette(n = 4, name = "Darjeeling1")),
                               # rev(wes_palette(n = 4, name = "Darjeeling2"))
                               # ),
                     # na.value = "white"
  # ) +
  scale_fill_manual("",values = c("#5BBCD6","#5BBCD6","#00A08A","#00A08A","#F2AD00","#F2AD00","#FF0000","#FF0000"),
  na.value = "white"
  ) +
  # scale_fill_manual(values = rev(wes_palette(n = 5, name = "Darjeeling1")),
  #                    na.value = "white"
  # ) +
  ggtheme_map()

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

# Set a number of 'empty bar' to add at the end of each group
empty_bar <- 8
to_add <- data.frame( matrix(NA, empty_bar*nlevels(Char), ncol(Species_Data)) )
colnames(to_add) <- colnames(Species_Data)
to_add$group <- rep(levels(Char), each=empty_bar)
Species_Data <- rbind(Species_Data, to_add)
Species_Data <- Species_Data %>% arrange(group,value)
Species_Data$id <- seq(1, nrow(Species_Data))

@@

>>>>

## Estimating Neighbourds

@@

## Determine Species Status

### Function `EstSppStatus`

  Data <- GetSppDist(Spp, Model = "SAU_C", Coord = Coord) %>% 
    set_names(c(seq(1950,2014,1),"INDEX","Species","Longitude","Latitude")) %>% 
    gather("Year","Value",`1950`:`2014`) %>%
    arrange(INDEX) %>% 
    left_join(Index_Code,
              by = "INDEX") %>% 
    filter(!is.na(EEZID),
           Value > 0) %>% 
    group_by(TaxonKey=Species,Year,Territory) %>% # Total catch per country
    summarise(Total_Catch = sum(Value,na.rm=T)) %>% 
    group_by(TaxonKey,Territory,Year) %>% 
    mutate(RMean = rollmean(x = Total_Catch, 3,
                            align = "right",
                            fill = Total_Catch)
           ) %>% # Running mean
    select(-Total_Catch) %>% 
    ungroup() %>% 
    mutate(Year = as.numeric(Year))

  # Tresholds to evaluate stocks if these are not met, then soecies status = "No Status"
  Tresholds_Data <- Data %>% 
    arrange(Territory) %>% 
    group_by(TaxonKey,Territory, grp = cumsum(c(1, diff(Year) != 65))) %>% 
    group_by(TaxonKey,Territory) %>% 
    summarise(Years_appart = ifelse(max(Year)-min(Year) >= 0,"Yes","No"), # Step 1. first and last reported landings are at least 10 years apart
              Consecutive = ifelse(max(grp) >= 5,"Yes","No"), # Step 2. There are at least 5 consecutive catch years
              Catch_over = ifelse(max(RMean >= 1000),"Yes","No") # Step 3. 3) The catch in a particular area (LME) is at least 1,000 tonnes.
    ) %>% 
    gather("Step","Treshold",Years_appart:Catch_over) %>% 
    group_by(TaxonKey,Territory) %>% 
    summarise(Met_Criteria = paste(unique(Treshold),collapse =";")
              )

    No_Status_Data <- Tresholds_Data %>% 
      filter(Met_Criteria != "Yes") %>% 
      select(TaxonKey,Territory) %>% 
      mutate(Status = "No Status")

    # Get Variables to perform status metric
    Status_Data <- Data %>% 
      anti_join(No_Status_Data, # Removes no status data
                by = c("TaxonKey","Territory")
      ) %>% 
      # Get Max catch and max catch year
      group_by(TaxonKey,Territory) %>% 
      top_n(1,RMean) %>% 
      rename(Max_Peak = RMean,
             Y_Max_Peak = Year) %>% 
      # Get Min catch after peak catch
      left_join(Data,
                by = c("TaxonKey","Territory")
                ) %>% 
      filter(Year > Y_Max_Peak) %>% 
      group_by(TaxonKey,Territory) %>% 
      top_n(-1,RMean) %>% 
      rename(Post_Max_Min = RMean,
             Y_Post_Max_Min = Year) %>% 
      left_join(Data,
                by = c("TaxonKey","Territory")
                ) %>% 
      # Final Evaluation 
      mutate(Status = ifelse(Year > Y_Post_Max_Min & Post_Max_Min < (Max_Peak*0.10) & (RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50)),"Rebuilding",
                             ifelse((Year < Y_Max_Peak & RMean <= (Max_Peak*0.50) | Y_Max_Peak == max(Year)),"Developing",
                                    ifelse(RMean > Max_Peak*0.50,"Max Exploited",
                                           ifelse(Year > Y_Max_Peak & (RMean > (Max_Peak*0.10) & RMean < (Max_Peak*0.50)),"Over Exploited",
                                                  ifelse(Year > Y_Max_Peak & RMean < Max_Peak*0.10,"Collapsed",
                                                         "No Status")
                                           )
                                    )
                             )
      )
      ) %>% 
      filter(Year > 2004) %>% # last 10 years of data
      group_by(TaxonKey,Territory,Status) %>% 
      summarise(n_Status= n()) %>% 
      group_by(TaxonKey,Territory) %>% 
      top_n(1,n_Status) %>%
      select(-n_Status)

### Data Species Status

### Sub routine for Species Status

```{r spp_status_data eval = T, echo = F}

```{r species_status_routine eval = T, echo = F}
# Needs to have trans species 
Species_Status <- bind_rows(
    mclapply(
      Species_List,
      FUN = EstSppStatus,
      Coord = CoorG  # Gabriels coordinate system for read species dist
    )
  )

# x <-Species_Status %>% 
#   group_by(Territory,Status) %>% 
#   summarise(n())

write.csv(Species_Status,
          paste(Data_Path,"Distribution_Data/Species_Status.csv",sep=""),
                row.names = F)

## Estimate Transboundary Species

@@

@@

  # Read SAu Status Data
  Status_Data <- fread(paste(Data_Path,"Distribution_Data/Species_Status.csv", sep ="")) %>% 
    rename(TaxonKey = Species)

@@

# Data per Territory
Transboundary_Spp <- Tresholded_T_Data %>% 
  group_by(Territory) %>% 
  summarise(
    n_trans_spp = length(unique(TaxonKey)),
    n_Neighbours = length(unique(Neighbour)),
    Trans_Rate = n_trans_spp/n_Neighbours
    ) %>% 
  mutate(
  Bins = cut(n_trans_spp,breaks = 4),
  Bins_Plot = cut(n_trans_spp,breaks = 4,
             labels = c('super low', 'low', 'high','super high'))
  )

@@

# Get Catch and Revenue data for mapping

Revenue_Country <- sau_eez_fes %>% 
  group_by(fishing_entity_id, Territory = fishing_entity) %>% 
  summarise(n=n()) %>% 
  select(-n) %>% 
  left_join(Tresholded_T_Data_x) %>% 
  left_join(Sau_Revenue_Data) %>% 
  group_by(Territory) %>% 
  summarise(Total_USD = (sum(Mean_Value,na.rm=T))/1000000) %>% 
  mutate(Territory = ifelse(Territory == "USA","United States of America",Territory),
         Bins = cut(Total_USD,breaks = 4),
         Bins_Plot = cut(Total_USD,breaks = 4,
                    labels = c('super low', 'low','high','super high'))
         ) %>% 
  filter(Total_USD > 0)

@@

# Transboundary Species shapefile
World_sf_si <- World_sf %>%
  st_transform(crs = 4326) %>% # 4326
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>%
  left_join(Transboundary_Spp, by ="Territory")

# Total catch/Revenue shapefile
World_sf_si_land <- World_land_sf %>%
  st_transform(crs = 4326) %>% # 4326
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>% 
  left_join(Revenue_Country, by ="Territory")

@@

# Make map
Plot <- ggplot() +
  geom_sf(data = World_sf_si_land,aes(fill = reorder(Bins_Plot,Total_USD)), colour = "grey80",size = 0.1) +
  geom_sf(data = World_sf_si,aes(fill =  reorder(Bins_Plot,n_trans_spp)),colour = "grey20", size = 0.1) + # n_trans_spp or Bins
  geom_sf(data = Grey_land,aes(fill = Bins),fill = "grey80", colour = "grey50",size = 0.1) + # n_trans_spp or Bins
  # scale_fill_gradientn(colours = pal,
  #                      na.value = "white") +
  # scale_fill_manual(values = c(rev(wes_palette(n = 4, name = "Darjeeling1")),
                               # rev(wes_palette(n = 4, name = "Darjeeling2"))
                               # ),
                     # na.value = "white"
  # ) +
  scale_fill_manual("",values = c("#5BBCD6",#"#5BBCD6", # blue
                                  "#00A08A",#"#00A08A", #green
                                  "#F2AD00",#"#F2AD00", # Yellow
                                  # "#F98400",#"#F98400", #Orange
                                  "#FF0000"#,"#FF0000" #Red
                                  ),
  na.value = "white"
  ) +
  # scale_fill_manual(values = rev(wes_palette(n = 5, name = "Darjeeling1")),
  #                    na.value = "white"
  # ) +
  ggtheme_map()

@@

# -------------------------- #
# Stock status Data
# -------------------------- #

Status_Data_Plot <- Tresholded_T_Data %>% 
  mutate(TaxonKey = as.character(TaxonKey)) %>% 
  # rename(Territory = CT_fishing_entity) %>% 
  left_join(Status_Data, 
            by =c("Territory","TaxonKey")
            ) %>%
  mutate(Status = ifelse(is.na(Status),"No Status",Status)) %>% 
  group_by(Territory,Status) %>% 
  summarise(value = length(unique(TaxonKey))) %>% 
  left_join(UN_Regions, by ="Territory") %>%
  mutate(Georegion = ifelse(is.na(georegion),"Other",paste(georegion))) %>% 
  rename(FishingRegion=Territory) %>% 
  left_join(Clean_sau_eez_fes) %>% 
  group_by(individual = fishing_entity,
           group = Georegion,
           observation = Status) %>% 
  summarise(Total_trans = sum(value,na.rm=T)) %>% 
  mutate(value = ifelse(Total_trans > 100,100,Total_trans)) %>% 
  filter(!is.na(individual)) %>% 
  select(individual,observation,group,value) %>% 
  arrange(group,value) %>% 
  mutate(value = ifelse(observation %in% c("Collapsed","Over Exploited"),value*-1,value))

@@

```{r}

data <- data.frame(
  individual=paste( "Mister ", seq(1,60), sep=""),
  group=c( rep('A', 10), rep('B', 30), rep('C', 14), rep('D', 6)) ,
  value1=sample( seq(10,100), 60, replace=T),
  value2=sample( seq(10,100), 60, replace=T),
  value3=sample( seq(10,100), 60, replace=T)
)

# Transform data in a tidy format (long format)
data <- data %>% gather(key = "observation", value="value", -c(1,2))

# Set a number of 'empty bar' to add at the end of each group
empty_bar <- 2
nObsType <- nlevels(as.factor(data$observation))
to_add <- data.frame( matrix(NA, empty_bar*nlevels(data$group)*nObsType, ncol(data)) )
colnames(to_add) <- colnames(data)
to_add$group <- rep(levels(data$group), each=empty_bar*nObsType )
data <- rbind(data, to_add)
data <- data %>% arrange(group, individual)
data$id <- rep( seq(1, nrow(data)/nObsType) , each=nObsType)

# Get the name and the y position of each label
label_data <- data %>% group_by(id, individual) %>% summarize(tot=sum(value))
number_of_bar <- nrow(label_data)
angle <- 90 - 360 * (label_data$id-0.5) /number_of_bar     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
label_data$hjust <- ifelse( angle < -90, 1, 0)
label_data$angle <- ifelse(angle < -90, angle+180, angle)

# prepare a data frame for base lines
base_data <- data %>% 
  group_by(group) %>% 
  summarize(start=min(id), end=max(id) - empty_bar) %>% 
  rowwise() %>% 
  mutate(title=mean(c(start, end)))

# prepare a data frame for grid (scales)
grid_data <- base_data
grid_data$end <- grid_data$end[ c( nrow(grid_data), 1:nrow(grid_data)-1)] + 1
grid_data$start <- grid_data$start - 1
grid_data <- grid_data[-1,]

# Make the plot
ggplot(data) +

  # Add the stacked bar
  geom_bar(aes(x=as.factor(id), y=value, fill=observation), stat="identity", alpha=0.5) +
  scale_fill_viridis(discrete=TRUE) +

  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
  geom_segment(data=grid_data, aes(x = end, y = 0, xend = start, yend = 0), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 50, xend = start, yend = 50), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 100, xend = start, yend = 100), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 150, xend = start, yend = 150), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 200, xend = start, yend = 200), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +

  # Add text showing the value of each 100/75/50/25 lines
  ggplot2::annotate("text", x = rep(max(data$id),5), y = c(0, 50, 100, 150, 200), label = c("0", "50", "100", "150", "200") , color="grey", size=6 , angle=0, fontface="bold", hjust=1) +

  ylim(-150,max(label_data$tot, na.rm=T)) +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = unit(rep(-1,4), "cm") 
  ) +
  coord_polar() +

  # Add labels on top of each bar
  geom_text(data=label_data, aes(x=id, y=tot+10, label=individual, hjust=hjust), color="black", fontface="bold",alpha=0.6, size=5, angle= label_data$angle, inherit.aes = FALSE ) +

  # Add base line information
  geom_segment(data=base_data, aes(x = start, y = -5, xend = end, yend = -5), colour = "black", alpha=0.8, size=0.6 , inherit.aes = FALSE )  +
  geom_text(data=base_data, aes(x = title, y = -18, label=group), hjust=c(1,1,0,0), colour = "black", alpha=0.8, size=4, fontface="bold", inherit.aes = FALSE)

@@

# Set a number of 'empty bar' to add at the end of each Georegion
Char <- as.factor(Status_Data_Plot$group) # Set groups to factors

##### COPY PASTE

# Transform data in a tidy format (long format)
data <- Status_Data_Plot

# Set a number of 'empty bar' to add at the end of each group
empty_bar <- 5
nObsType <- nlevels(as.factor(data$observation))
to_add <- data.frame( matrix(NA, empty_bar*nlevels(Char)*nObsType, ncol(data)) )
colnames(to_add) <- colnames(data)
to_add$group <- rep(levels(Char), each=empty_bar*nObsType)
to_add$individual <- rep(letters[1:6], each=empty_bar*nObsType)
data <- bind_rows(data, to_add)
data <- data %>% arrange(group, individual) %>% rowwise() %>%  mutate(id = as.numeric(as.factor(individual)))
data$id <- as.numeric(as.factor(data$individual))

# Get the name and the y position of each label
label_data <- data %>% group_by(id, individual) %>% summarize(tot=sum(value))
number_of_bar <- nrow(label_data)
angle <- 90 - 360 * (label_data$id-0.5) /number_of_bar     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
label_data$hjust <- ifelse( angle < -90, 1, 0)
label_data$angle <- ifelse(angle < -90, angle+180, angle)

# prepare a data frame for base lines
base_data <-  data %>% 
  group_by(group) %>% 
  summarize(start=min(id,na.rm=T), end=max(id,na.rm=T) - empty_bar) %>% 
  rowwise() %>% 
  mutate(title=mean(c(start, end)))

# prepare a data frame for grid (scales)
grid_data <- base_data
grid_data$end <- grid_data$end[ c( nrow(grid_data), 1:nrow(grid_data)-1)] + 1
grid_data$start <- grid_data$start - 1
grid_data <- grid_data[-1,]

data <- data %>% 
  ungroup() %>% 
  mutate(individual = ifelse(is.na(observation),NA,observation))

ggplot(data) + 
  # Add the stacked bar
  geom_bar(aes(x=as.factor(id), y=value, fill=observation), stat="identity", alpha=0.5) +
  scale_fill_manual("Continent",
                    values = c(wes_palette(n = 5, name = "Darjeeling1"),
                               wes_palette(n = 1, name = "Darjeeling2")
                    ),
                    na.value = "white"
  ) +

  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
  geom_segment(data=grid_data, aes(x = end, y = 0, xend = start, yend = 0), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 50, xend = start, yend = 50), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 100, xend = start, yend = 100), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 150, xend = start, yend = 150), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 200, xend = start, yend = 200), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +

  # Add text showing the value of each 100/75/50/25 lines
  ggplot2::annotate("text", x = rep(max(data$id),5), y = c(0, 50, 100, 150, 200), label = c("0", "50", "100", "150", "200") , color="grey", size=6 , angle=0, fontface="bold", hjust=1) +

  ylim(-150,max(label_data$tot, na.rm=T)) +
  theme_minimal() +
  theme(
    legend.position = "right",
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = unit(rep(-1,4), "cm") 
  ) +
  coord_polar() +

  # Add labels on top of each bar
  geom_text(data=label_data, aes(x=id, y=max(tot,na.rm=T), label=individual, hjust=hjust), color="black", fontface="bold",alpha=0.6, size=2, angle= label_data$angle, inherit.aes = FALSE ) +

  # Add base line information
  geom_segment(data=base_data, aes(x = start, y = -5, xend = end, yend = -5), colour = "black", alpha=0.8, size=0.6 , inherit.aes = FALSE )  +
  geom_text(data=base_data, aes(x = title, y = -18, label=group), hjust=c(1,1,1,0,0,0), colour = "black", alpha=0.8, size=4, fontface="bold", inherit.aes = FALSE)

#### END COPY PASTE

empty_bar <- 5
nObsType <- nlevels(as.factor(Status_Data_Plot$observation))
to_add <- data.frame( matrix(NA, empty_bar*nlevels(Char)*nObsType, ncol(Status_Data_Plot)) )
colnames(to_add) <- colnames(Status_Data_Plot)
to_add$group <- rep(levels(Char), each=empty_bar*nObsType)
Status_Data_Plot <- bind_rows(Status_Data_Plot, to_add)
Status_Data_Plot <- Status_Data_Plot %>% arrange(group, individual)
# Status_Data_Plot$id <- c(rep(seq(1,round(nrow(Status_Data_Plot)/nObsType)) , each=nObsType),128)
Status_Data_Plot$id <- as.numeric(as.factor(Status_Data_Plot$individual))

@@

# Top n of each group label
Top_Countries <- Status_Data_Plot %>% 
  group_by(group) %>% 
  top_n(5,value)

# Create labels for all but top 5
# Get the name and the y position of each label

label_data <- Status_Data_Plot %>% 
  group_by(id, individual) %>% 
  summarize(tot=sum(value))

label_data <- Status_Data_Plot 
number_of_bar <- nrow(label_data)
angle <- 90 - 360 * (label_data$id-0.5) /number_of_bar     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
label_data$hjust <- ifelse( angle < -90, 1, 0)
label_data$angle <- ifelse(angle < -90, angle+180, angle)

@@

# prepare a data frame for base lines
base_data <- Status_Data_Plot %>% 
  group_by(group) %>% 
  summarize(start=min(id,na.rm=T), 
            end=max(id,na.rm=T) - empty_bar, 
            median = median(value, na.rm = T)
            ) %>% 
  rowwise() %>% 
  mutate(title=mean(c(start, end)))

# prepare a data frame for grid (scales)
grid_data <- base_data
grid_data$end <- grid_data$end[ c( nrow(grid_data), 1:nrow(grid_data)-1)] + 1
grid_data$start <- grid_data$start - 1
# grid_data[1,2] <- 5 # Manually include Africa for the median
# grid_data[1,3] <- 1

@@

# Global Variables
Seq_axis <- seq(0,100,20)
Plot_Limit <- max(Status_Data_Plot$value,na.rm=T)
Plot_Limit_Low <- -50
Ticks_Color <- "grey50"

ggplot(Status_Data_Plot) +

  # Add the stacked bar
  geom_bar(aes(x=as.factor(id), y=value, fill=observation), stat="identity", alpha=0.5) +
  # scale_fill_viridis(discrete=TRUE) +

  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
  geom_segment(data=grid_data, aes(x = end, y = 0, xend = start, yend = 0), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 50, xend = start, yend = 50), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 100, xend = start, yend = 100), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 150, xend = start, yend = 150), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 200, xend = start, yend = 200), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +

  # Add text showing the value of each 100/75/50/25 lines
  ggplot2::annotate("text", x = rep(max(Status_Data_Plot$id,na.rm=T),5), y = c(0, 50, 100, 150, 200), label = c("0", "50", "100", "150", "200") , color="grey", size=6 , angle=0, fontface="bold", hjust=1) +

  ylim(-150,max(label_data$value, na.rm=T)) +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = unit(rep(-1,4), "cm") 
  ) +
  coord_polar() +

  # Add labels on top of each bar
  geom_text(data=label_data, aes(x=id, y=value+10, label=individual, hjust=hjust), color="black", fontface="bold",alpha=0.6, size=5, angle= label_data$angle, inherit.aes = FALSE ) +

  # Add base line information
  geom_segment(data=base_data, aes(x = start, y = -5, xend = end, yend = -5), colour = "black", alpha=0.8, size=0.6 , inherit.aes = FALSE )  +
  geom_text(data=base_data, aes(x = title, y = -18, label=group), hjust=c(1,1,0,0,1,1), colour = "black", alpha=0.8, size=4, fontface="bold", inherit.aes = FALSE)

@@

ggplot(Status_Data_Plot,

@@

           fill=observation)

@@

               fill=observation),

@@

  geom_segment(data=grid_data, aes(x = end, y = 0, xend = start, yend = 0), colour = "black", alpha=0, size=0.3 , inherit.aes = FALSE ) +

@@

  # geom_segment(data=median_data,
  #              aes(x = end,
  #                  y = median,
  #                  xend = start+5, 
  #                  yend = median,
  #                  colour = group),
  #              alpha=1,
  #              size=0.5 , 
  #              inherit.aes = FALSE ) +

@@

           x = rep(max(Status_Data_Plot$id),length(Seq_axis)),

@@

  ylim(-150,max(label_data$value, na.rm=T)) +
    legend.position = "none",

@@

            aes(x=id,
                y=Plot_Limit,

@@

  coord_polar()

@@

    # legend.position = "",

@@

                               wes_palette(n = 4, name = "Darjeeling2"),
                               "black","grey","blue"

@@

# Set a number of 'empty bar' to add at the end of each group
empty_bar <- 2
to_add <- data.frame( matrix(NA, empty_bar*nlevels(Char), ncol(Species_Data)) )
colnames(to_add) <- colnames(Species_Data)
to_add$group <- rep(levels(Char), each=empty_bar)
Species_Data <- rbind(Species_Data, to_add)
Species_Data <- Species_Data %>% arrange(group,value)
Species_Data$id <- seq(1, nrow(Species_Data))

@@

# ggsave(
#     plot = last_plot(),
#     width = 12,
#     height = 12,
#     units = "in",
#     filename = "Territory_circular_both.png",
#     path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/"
#   )
